### 2018-03-29 README.Rmd
add librsvg to rmd

Ubuntu/Debian:
```
sudo apt-get install libudunits2-dev libgsl-dev libsdl1.2-dev libreadline-dev imagemagick libfftw3-dev libudunits2-dev -y
sudo apt-get install python2.7-dev python3-dev python3-pip
pip3 install --user virtualenv numpy matplotlib pandas six jinja2 python-dateutil pytz pyparsing cycler tqdm python-igraph rpy2 Cython scipy statsmodels sklearn seaborn
```

Fedora/CentOS:
```
sudo dnf install openssl-devel libcurl-devel udunits2-devel libxml2-devel gsl-devel SDL2-devel readline-devel ImageMagick-c++-devel SDL-devel python2-devel python3-devel python3-pip python3-matplotlib-tk openblas-devel lapack-devel
pip3 install --user virtualenv numpy matplotlib pandas six jinja2 python-dateutil pytz pyparsing cycler tqdm python-igraph rpy2 Cython scipy statsmodels sklearn seaborn
Rscript -e 'install.packages("udunits2", configure.args =  c(udunits2 = '--with-udunits2-include=/usr/include/udunits2'))'
```

>>>>

Ubuntu/Debian:
```
sudo apt-get install libudunits2-dev libgsl-dev libsdl1.2-dev libreadline-dev imagemagick libfftw3-dev libudunits2-dev librsvg2-dev -y
sudo apt-get install python2.7-dev python3-dev python3-pip
pip3 install --user virtualenv numpy matplotlib pandas six jinja2 python-dateutil pytz pyparsing cycler tqdm python-igraph rpy2 Cython scipy statsmodels sklearn seaborn
```

Fedora/CentOS:
```
sudo dnf install openssl-devel libcurl-devel udunits2-devel libxml2-devel gsl-devel SDL2-devel readline-devel ImageMagick-c++-devel SDL-devel python2-devel python3-devel python3-pip python3-matplotlib-tk openblas-devel lapack-devel librsvg2-devel
pip3 install --user virtualenv numpy matplotlib pandas six jinja2 python-dateutil pytz pyparsing cycler tqdm python-igraph rpy2 Cython scipy statsmodels sklearn seaborn
Rscript -e 'install.packages("udunits2", configure.args =  c(udunits2 = '--with-udunits2-include=/usr/include/udunits2'))'
```

macOS:

Install SDL2 and SDL1.2 manually.

Install `librsvg` with brew.
